Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-22 paper/ms.tex
update ms; fix fig13 typo

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.55\textwidth]{f13.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Brightnesses and distances of our CPVs compared
      against previous work.}  
      ``K2 literature'' corresponds to \citet{2017AJ....153..152S} and
      \citet{2018AJ....155...63S}.  ``TESS literature'' corresponds to
      \citet{2019ApJ...876..127Z,2021AJ....161...60S,2022AJ....163..144G}, and \citet{2023ApJ...945..114P}.
      ``CQVs'' and ``candidates'' are as in
      Figure~\ref{fig:catalogscatter}, though for visual clarity
      unresolved binaries are not highlighted.  PTFO 8-8695, a CPV at
      a distance of $\approx$350\,pc, is not shown.
		}
			\vspace{-0.5cm}
		\label{fig:tmagvsdist}
	\end{center}
\end{figure}

{\it How do the brightness and distance distributions
compare?}---Figure~\ref{fig:tmagvsdist} compares the TESS magnitudes
and distances for the CPVs in Table~\ref{tab:thetable} against the
previously known literature CPVs.  At the extremes, our new sources
include the closest and brightest CPVs currently known. 
All K2 CPVs are in Sco-Cen,
$\approx$100-180\,pc from the Sun.  The large gap in the TESS literature CPV
distance distribution was because the studies by
\citep{2019ApJ...876..127Z} and \citet{2023ApJ...945..114P} both
favored Tuc-Hor; many of our new CQVs are within this 40-100\,pc gap.

>>>>

\begin{figure}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.55\textwidth]{f13.pdf}
		\vspace{-0.2cm}
		\caption{
			{\bf Brightnesses and distances of our CPVs compared
      against previous work.}  
      ``K2 literature'' corresponds to \citet{2017AJ....153..152S} and
      \citet{2018AJ....155...63S}.  ``TESS literature'' corresponds to
      \citet{2019ApJ...876..127Z,2021AJ....161...60S,2022AJ....163..144G}, and \citet{2023ApJ...945..114P}.
      ``\replaced{CQVs}{CPVs}'' and ``candidates'' are as in
      Figure~\ref{fig:catalogscatter}, though for visual clarity
      unresolved binaries are not highlighted.  PTFO 8-8695, a CPV at
      a distance of $\approx$350\,pc, is not shown.
		}
			\vspace{-0.5cm}
		\label{fig:tmagvsdist}
	\end{center}
\end{figure}

{\it How do the brightness and distance distributions
compare?}---Figure~\ref{fig:tmagvsdist} compares the TESS magnitudes
and distances for the CPVs in Table~\ref{tab:thetable} against the
previously known literature CPVs.  At the extremes, our new sources
include the closest and brightest CPVs currently known. 
All K2 CPVs are in Sco-Cen,
$\approx$100-180\,pc from the Sun.  The large gap in the TESS literature CPV
distance distribution was because the studies by
\citep{2019ApJ...876..127Z} and \citet{2023ApJ...945..114P} both
favored Tuc-Hor; many of our new \replaced{CQVs}{CPVs} are within this 40-100\,pc gap.
